---
title: "Mapping the Peaks R Notebook"
output:
  html_document: default
  html_notebook: default
---

Figure 1, showing fitness across the adaptation phase. Also shows a boxplot comparing the fitness from the end of the initial phase and the end of the adaptation phase.

```{r, message=FALSE}
# Load the libraries
library(plyr)
library(tidyverse)
library(stringr)
library(reshape2)
library(cowplot)
library(scales)

# Misc functions
se <- function(arr) {
  return(sd(arr) / sqrt(len(arr)))
}
maxsd <- function(xarr) {
  return(mean(xarr) + sd(xarr))
}
minsd <- function(xarr) {
  return(mean(xarr) - sd(xarr))
}
bootmean <- function(data, indices) {
  return(mean(data[indices]))
}

```

```{r, results='hold'}

# Avg Columns
avgcols = cols(
  X1 = col_integer(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double(),
  X11 = col_double(),
  X12 = col_double(),
  X13 = col_double(),
  X14 = col_double(),
  X15 = col_double(),
  X16 = col_double(),
  X17 = col_double(),
  X18 = col_character(),
  X19 = col_double(),
  X20 = col_integer()
)

# Dom Columns
domcols = cols(
  X1 = col_integer(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_integer(),
  X7 = col_integer(),
  X8 = col_integer(),
  X9 = col_double(),
  X10 = col_integer(),
  X11 = col_double(),
  X12 = col_double(),
  X13 = col_double(),
  X14 = col_double(),
  X15 = col_double(),
  X16 = col_character(),
  X17 = col_double(),
  X18 = col_character(),
  X19 = col_double(),
  X20 = col_integer()
)

avgnamescols <- c(
  X1 = "Update",
  X2 = "Merit",
  X3 = "GestationTime",
  X4 = "Fitness",
  X5 = "RepRate",
  X6 = "Size",
  X7 = "CopiedSize",
  X8 = "ExecSize",
  X9 = "Abundance",
  X10 = "PropGaveBirth",
  X11 = "PropBreedTrue",
  X12 = "GenotypeDepth",
  X13 = "Generation",
  X14 = "NeutralMetric",
  X15 = "LineageLabel",
  X16 = "TrueRepRate",
  X17 = "Broken",
  X18 = "Replicate",
  X19 = "EndOfInitFit",
  X20 = "IndexInAvgFile"

)

fr_popA <- read_delim("./data/final_run_AB_popA_recomb_ave.dat", " ",
                        escape_double = FALSE, col_names = FALSE, trim_ws = TRUE, skip = 22, col_types = avgcols)
fr_popA$pop = "Fit"
fr_popA <- plyr::rename(fr_popA, avgnamescols)

fr_popB <- read_delim("./data/final_run_AB_popB_recomb_ave.dat", " ",
                        escape_double = FALSE, col_names = FALSE, trim_ws = TRUE, skip = 22, col_types = avgcols)
fr_popB$pop = "Flat"
fr_popB <- plyr::rename(fr_popB, avgnamescols)

fr_AB <- rbind(fr_popA, fr_popB)
```

```{r}
fr_adapt_fit <- ggplot(data = fr_AB) +
  labs(x = "Generations", y = expression(W[avg]/W[initial]), color = "", fill = "") +
  background_grid(major = "xy", minor = "none") +
  stat_summary_bin(geom = "ribbon", fun.ymin = minsd, fun.ymax = maxsd, binwidth = 25, alpha = 0.5, aes(x = Generation, y = Fitness/EndOfInitFit, fill = pop)) +
  stat_summary_bin(geom = "line", fun.y = mean, binwidth = 25, aes(x = Generation, y = Fitness/EndOfInitFit, color = pop)) +
  scale_color_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  scale_fill_manual(values = c(Fit = "lightblue", Flat = "lightpink")) +
  scale_y_log10()

fr_adapt_fit

```

Fitness before and after boxplots.
```{r}
statscols <- cols(
  name = col_character(),
  viable = col_integer(),
  merit = col_double(),
  gestation_time = col_integer(),
  fitness = col_double(),
  errors = col_integer(),
  genome_size = col_integer(),
  copied_size = col_integer(),
  executed_size = col_integer(),
  task_str = col_integer(),
  task_count = col_integer()
)

fr_init_stats <- read_csv("./data/final_run_init_stats.csv", col_types = statscols)
fr_init_stats$pop <- "Initial"
fr_popA_stats <- read_csv("./data/final_run_popA_stats.csv", col_types = statscols)
fr_popA_stats$pop <- "Fit"
fr_popB_stats <- read_csv("./data/final_run_popB_stats.csv", col_types = statscols)
fr_popB_stats$pop <- "Flat"

fr_stats <- plyr::rbind.fill(fr_init_stats, fr_popA_stats, fr_popB_stats)

comp_fit_bplot <- ggplot(fr_stats, aes(x = pop, y = fitness, fill = pop)) +
  geom_boxplot(notch = TRUE) +
  scale_y_log10(labels = trans_format("log10", math_format(10^.x))) +
  labs(x = "", y = "Fitness", fill = "") + 
  scale_x_discrete(limits = c("Initial", "Fit", "Flat")) +
  scale_fill_manual(values = c("Fit" = "dodgerblue", "Flat" = "firebrick1", "Initial" = "mediumorchid")) +
  guides(fill=FALSE)

comp_fit_bplot
```

Misc. boxplots, may not use.
```{r}
comp_tasks_bplot <- ggplot(fr_stats, aes(x = pop, y = errors, fill = pop)) +
  geom_boxplot(notch = TRUE) +
  scale_y_log10() +
  labs(x = "", y = "Errors", fill = "") +
  scale_x_discrete(limits = c("Initial", "Fit", "Flat")) +
  scale_fill_manual(values = c("Fit" = "dodgerblue", "Flat" = "firebrick1", "Initial" = "mediumorchid")) +
  guides(fill=FALSE)

comp_gest_bplot <- ggplot(fr_stats, aes(x = pop, y = gestation_time, fill = pop)) +
  geom_boxplot(notch = TRUE) +
  labs(x = "", y = "Gestation Time", fill = "") + 
  scale_x_discrete(limits = c("Initial", "Fit", "Flat")) +
  scale_fill_manual(values = c("Fit" = "dodgerblue", "Flat" = "firebrick1", "Initial" = "mediumorchid")) +
  guides(fill=FALSE)

comp_exec_bplot <- ggplot(fr_stats, aes(x = pop, y = executed_size, fill = pop)) +
  geom_boxplot(notch = TRUE) +
  labs(x = "", y = "Executed Size", fill = "") + 
  scale_x_discrete(limits = c("Initial", "Fit", "Flat")) +
  scale_fill_manual(values = c("Fit" = "dodgerblue", "Flat" = "firebrick1", "Initial" = "mediumorchid")) +
  guides(fill=FALSE)

comp_tasks_bplot
comp_gest_bplot
comp_exec_bplot

#exsize_gest_plt <- ggdraw() + draw_plot(comp_gest_bplot, x = 0, y = 0, width = 0.5, height = 1) +
#  draw_plot(comp_exec_bplot, x = 0.5, y = 0, width = 0.5, height = 1) + draw_plot_label(c("a", "b"), c(0, 0.5), c(1, 1))
#ggsave(exsize_gest_plt, filename = "S1ExecGestPlt.pdf", device = cairo_pdf, width = 9, height = 5)
```
Test statistics for comparison.
```{r}
wilcox.test(filter(fr_stats, pop == "Initial")$fitness, filter(fr_stats, pop == "Fit")$fitness)
wilcox.test(filter(fr_stats, pop == "Fit")$fitness, filter(fr_stats, pop == "Flat")$fitness)
wilcox.test(filter(fr_stats, pop == "Initial")$fitness, filter(fr_stats, pop == "Flat")$fitness)

wilcox.test(filter(fr_stats, pop == "Initial")$errors, filter(fr_stats, pop == "Fit")$errors)
wilcox.test(filter(fr_stats, pop == "Fit")$errors, filter(fr_stats, pop == "Flat")$errors)
wilcox.test(filter(fr_stats, pop == "Initial")$errors, filter(fr_stats, pop == "Flat")$errors)

wilcox.test(filter(fr_stats, pop == "Initial")$gestation_time, filter(fr_stats, pop == "Fit")$gestation_time)
wilcox.test(filter(fr_stats, pop == "Fit")$gestation_time, filter(fr_stats, pop == "Flat")$gestation_time)
wilcox.test(filter(fr_stats, pop == "Initial")$gestation_time, filter(fr_stats, pop == "Flat")$gestation_time)

wilcox.test(filter(fr_stats, pop == "Initial")$executed_size, filter(fr_stats, pop == "Fit")$executed_size)
wilcox.test(filter(fr_stats, pop == "Fit")$executed_size, filter(fr_stats, pop == "Flat")$executed_size)
wilcox.test(filter(fr_stats, pop == "Initial")$executed_size, filter(fr_stats, pop == "Flat")$executed_size)

```

Figure 1
```{r}
fit_combo_plt <- ggdraw() + draw_plot(comp_fit_bplot, x = 0, y = 0, width = 0.3, height = 1) +
  draw_plot(fr_adapt_fit, x = 0.3, y = 0, width = 0.7, height = 1) + draw_plot_label(c("a", "b"), c(0.01, 0.31), c(0.95, 0.95))
ggsave(fit_combo_plt, filename = "Fig1CombFitPlt.pdf", device = cairo_pdf, width = 8.5, height = 3)
fit_combo_plt
```

Figure 2, showing an example competition assay.
```{r}
# Load the libraries
library(tidyverse)
library(plyr)
library(reshape2)
library(cowplot)
library(scales)

# Misc functions
se <- function(arr) {
  return(sd(arr) / sqrt(len(arr)))
}
maxsd <- function(xarr) {
  return(mean(xarr) + sd(xarr))
}
minsd <- function(xarr) {
  return(mean(xarr) - sd(xarr))
}
bootmean <- function(data, indices) {
  return(mean(data[indices]))
}

# Avg Columns
avgcompcols = cols(
  X1 = col_integer(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double(),
  X11 = col_double(),
  X12 = col_double(),
  X13 = col_double(),
  X14 = col_double(),
  X15 = col_double(),
  X16 = col_double(),
  X18 = col_character(),
  X19 = col_character()
)

avgcompnamescols <- c(
  X1 = "Update",
  X2 = "Merit",
  X3 = "GestationTime",
  X4 = "Fitness",
  X5 = "RepRate",
  X6 = "Size",
  X7 = "CopiedSize",
  X8 = "ExecSize",
  X9 = "Abundance",
  X10 = "PropGaveBirth",
  X11 = "PropBreedTrue",
  X12 = "GenotypeDepth",
  X13 = "Generation",
  X14 = "NeutralMetric",
  X15 = "LineageLabel",
  X16 = "TrueRepRate",
  X17 = "Replicate",
  X18 = "SubReplicate",
  X19 = "MutRate"
)

comp_avg <- read_delim("./competition/replicate_3279_comp.dat", " ", escape_double = FALSE, trim_ws = TRUE, col_names = FALSE, col_types = avgcompcols)
comp_avg <- plyr::rename(comp_avg, avgcompnamescols)

mu0p5 <- ggplot(filter(comp_avg, MutRate == "0.5")) +
  stat_summary_bin(geom = "ribbon", fun.ymin = minsd, fun.ymax = maxsd, binwidth = 1, fill = "mediumaquamarine", aes(x = Generation, y = 1-LineageLabel/7)) +
  stat_summary_bin(geom = "line", fun.y = mean, binwidth = 1, aes(x = Generation, y = 1-LineageLabel/7)) +
  scale_y_continuous(limits = c(0, 1.0)) +
  labs(y = "Fraction Fit") +
  annotate('text', label = "μ = 0.5", x = 150, y = 0.75)

mu1p0 <- ggplot(filter(comp_avg, MutRate == "1.0")) +
  stat_summary_bin(geom = "ribbon", fun.ymin = minsd, fun.ymax = maxsd, binwidth = 1, fill = "mediumaquamarine", aes(x = Generation, y = 1-LineageLabel/7)) +
  stat_summary_bin(geom = "line", fun.y = mean, binwidth = 1, aes(x = Generation, y = 1-LineageLabel/7)) +
  scale_y_continuous(limits = c(0, 1.0)) +
  labs(y = "Fraction Fit") +
  annotate('text', label = "μ = 1.0", x = 150, y = 0.75)

mu1p5 <- ggplot(filter(comp_avg, MutRate == "1.5")) +
  stat_summary_bin(geom = "ribbon", fun.ymin = minsd, fun.ymax = maxsd, binwidth = 1, fill = "mediumaquamarine", aes(x = Generation, y = 1-LineageLabel/7)) +
  stat_summary_bin(geom = "line", fun.y = mean, binwidth = 1, aes(x = Generation, y = 1-LineageLabel/7)) +
  scale_y_continuous(limits = c(0, 1.0)) +
  labs(y = "Fraction Fit") +
  annotate('text', label = "μ = 1.5", x = 150, y = 0.75)

mu2p0 <- ggplot(filter(comp_avg, MutRate == "2.0")) +
  stat_summary_bin(geom = "ribbon", fun.ymin = minsd, fun.ymax = maxsd, binwidth = 1, fill = "mediumaquamarine", aes(x = Generation, y = 1-LineageLabel/7)) +
  stat_summary_bin(geom = "line", fun.y = mean, binwidth = 1, aes(x = Generation, y = 1-LineageLabel/7)) +
  scale_y_continuous(limits = c(0, 1.0)) +
  labs(y = "Fraction Fit") +
  annotate('text', label = "μ = 2.0", x = 150, y = 0.75)

combo_comp <- ggdraw() + draw_plot(mu0p5, 0, 0.5, 0.5, 0.5) + draw_plot(mu1p0, 0.5, 0.5, 0.5, 0.5) + draw_plot(mu1p5, 0, 0, 0.5, 0.5) +
  draw_plot(mu2p0, 0.5, 0, 0.5, 0.5) + draw_plot_label(label = c("a", "b", "c", "d"), c(0, 0.5, 0, 0.5), c(1.0, 1.0, 0.5, 0.5))

ggsave(combo_comp, filename = "Fig2CompPlt.pdf", device = cairo_pdf, width = 8, height = 5)
combo_comp
```

Figure 3, showing comparisons of single step mutations. Also calculates statistics for the comparisons.
```{r}
stepcoltypes <- cols(
  .default = col_double(),
  X1 = col_integer(),
  X11 = col_integer(),
  X12 = col_integer(),
  X15 = col_integer(),
  X21 = col_integer(),
  X22 = col_integer(),
  X23 = col_integer(),
  X24 = col_integer(),
  X25 = col_integer(),
  X26 = col_integer(),
  X27 = col_integer(),
  X28 = col_integer(),
  X29 = col_character(),
  X30 = col_character(),
  X31 = col_character(),
  X32 = col_character()
)

stepcolnames <- c(
  X1 = "Update",
  X2 = "Lethal",
  X3 = "Deleterious",
  X4 = "Slt.Deleterious",
  X5 = "AnyDel",
  X6 = "Neutral",
  X7 = "Beneficial",
  X8 = "AvgBenSize",
  X9 = "AvgDelSize",
  X10 = "AvgDelLethalSize",
  X11 = "TestedMutants",
  X12 = "Distance",
  X13 = "BaseFitness",
  X14 = "BaseMerit",
  X15 = "BaseGestation",
  X16 = "PeakFitness",
  X17 = "AvgFitness",
  X18 = "AvgSqFitness",
  X19 = "TotalS",
  X20 = "TotalComplex",
  X21 = "PLethalEpi",
  X22 = "PSynEpi",
  X23 = "PAntagEpi",
  X24 = "PNoEpi",
  X25 = "AvgSynEpiSize",
  X26 = "AvgAntagEpiSize",
  X27 = "AvgSizeNoEpi",
  X28 = "TotalEpiCount",
  X29 = "SuperRep",
  X30 = "StepNum",
  X31 = "Rep",
  X32 = "Duplicate"
)

frls_popA <- read_delim("./landscape/final_run_landscape_long_Fit.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)
frls_popB <- read_delim("./landscape/final_run_landscape_long_Flat.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)

frls_popA$pop <- "Fit"
frls_popB$pop <- "Flat"
frls_combo <- rbind(frls_popA, frls_popB)
frls_combo <- plyr::rename(frls_combo, stepcolnames)

frls_melted <- melt(frls_combo[c(2,3,4,5,6,7,30,31,33)], id.vars = c("pop", "StepNum", "Rep"))

onestep_melt <- filter(frls_melted, StepNum == '1one')
onestep_nonmelt <- subset(frls_combo, StepNum == '1one')

twostep_melt <- filter(frls_melted, StepNum == '2two')
twostep_nonmelt <- filter(frls_combo, StepNum == "2two")

# Tests for significance
one_lethal_comp <- wilcox.test(filter(onestep_melt, variable == "Lethal", pop == "Fit")$value, filter(onestep_melt, variable == "Lethal", pop == "Flat")$value)
one_del_comp <- wilcox.test(filter(onestep_melt, variable == "Deleterious", pop == "Fit")$value, filter(onestep_melt, variable == "Deleterious", pop == "Flat")$value)
one_sltdel_comp <- wilcox.test(filter(onestep_melt, variable == "Slt.Deleterious", pop == "Fit")$value, filter(onestep_melt, variable == "Slt.Deleterious", pop == "Flat")$value)
one_anydel_comp <- wilcox.test(filter(onestep_melt, variable == "AnyDel", pop == "Fit")$value, filter(onestep_melt, variable == "AnyDel", pop == "Flat")$value)
one_neut_comp <- wilcox.test(filter(onestep_melt, variable == "Neutral", pop == "Fit")$value, filter(onestep_melt, variable == "Neutral", pop == "Flat")$value)
one_ben_comp <- wilcox.test(filter(onestep_melt, variable == "Beneficial", pop == "Fit")$value, filter(onestep_melt, variable == "Beneficial", pop == "Flat")$value)
one_reldel_comp <- wilcox.test((filter(onestep_nonmelt, pop == "Fit")$AvgFitness / filter(onestep_nonmelt, pop == "Fit")$BaseFitness), (filter(onestep_nonmelt, pop == "Flat")$AvgFitness / filter(onestep_nonmelt, pop == "Flat")$BaseFitness))

two_del_comp <- wilcox.test(filter(onestep_melt, variable == "Deleterious", pop == "Flat")$value, filter(twostep_melt, variable == "Deleterious", pop == "Flat")$value)
two_del_comp

#formatter <- trans_format("log10", math_format(10^.x))

annotate_txt_size = 7

one_lethal <- ggplot(onestep_nonmelt, aes(x = pop, y = Lethal, fill = pop)) +
  geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("Fit", "Flat")) +
  guides(fill=FALSE) +
  annotate(geom = "text", label = "Lethal", x = 0.75, y = max(onestep_nonmelt$Lethal), size = annotate_txt_size)

one_del <- ggplot(onestep_nonmelt, aes(x = pop, y = Deleterious, fill = pop)) +
  geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("Fit", "Flat")) +
  guides(fill=FALSE)+
  annotate(geom = "text", label = "Deleterious", x = 0.75, y = max(onestep_nonmelt$Deleterious), size = annotate_txt_size)

one_sltdel <- ggplot(onestep_nonmelt, aes(x = pop, y = Slt.Deleterious, fill = pop)) +
  geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("", "")) +
  guides(fill=FALSE)+
  annotate(geom = "text", label = "Slt. Deleterious", x = 0.75, y = max(onestep_nonmelt$Slt.Deleterious), size = annotate_txt_size)

one_neut <- ggplot(onestep_nonmelt, aes(x = pop, y = Neutral, fill = pop)) +
  geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("", "")) +
  guides(fill=FALSE)+
  annotate(geom = "text", label = "Neutral", x = 0.75, y = max(onestep_nonmelt$Neutral), size = annotate_txt_size)

one_ben <- ggplot(onestep_nonmelt, aes(x = pop, y = Beneficial, fill = pop)) + geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("", "")) +
  guides(fill=FALSE)+
  annotate(geom = "text", label = "Beneficial", x = 0.75, y = max(onestep_nonmelt$Beneficial), size = annotate_txt_size)

one_relfit <- ggplot(onestep_nonmelt, aes(x = pop, y = AvgFitness/BaseFitness, fill = pop)) + geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  labs(x = "", y = "Relative Average Fitness", fill = "") +
  scale_x_discrete(labels = c("Fit", "Flat")) + guides(fill=FALSE) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) #+
  #annotate(geom = "text", label = "Avg. Rel. Fitness", x = 0.75, y = max(onestep_nonmelt$AvgFitness/onestep_nonmelt$BaseFitness), size = annotate_txt_size)

comb_one_plt <- ggdraw() + draw_plot(one_ben, 0, 0.5, 0.333, 0.5) + draw_plot(one_neut, 0.333, 0.5, 0.333, 0.5) + draw_plot(one_sltdel, 0.666, 0.5, 0.333, 0.5) +
  draw_plot(one_del, 0, 0, 0.333, 0.5) + draw_plot(one_lethal, 0.333, 0, 0.333, 0.5) + draw_plot(one_relfit, 0.666, 0, 0.333, 0.5) + draw_plot_label(label = c("a", "b", "c", "d", "e", "f"), c(0, 0.333, 0.666,0, 0.333, 0.666), c(1.0, 1.0, 1.0, 0.5, 0.5, 0.5), size = 25)

ggsave(filename = "Fig3OneStepComp.pdf", plot = comb_one_plt, device = cairo_pdf, width = 24, height = 10)

comb_one_plt

one_alldel <- ggplot(onestep_nonmelt, aes(x = pop, y = AnyDel, fill = pop)) +
  geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", fill = "") + 
  scale_color_manual(guide = FALSE, labels = c("One"), values = c("black")) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) +
  scale_x_discrete(labels=c("", "")) +
  guides(fill=FALSE)+
  annotate(geom = "text", label = "All Deleterious", x = 0.75, y = max(onestep_nonmelt$AnyDel), size = annotate_txt_size)

one_reldelsize <- ggplot(onestep_nonmelt, aes(x = pop, y = AvgDelSize/BaseFitness, fill = pop)) + geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  labs(x = "", y = "Relative Fitness of Deleterious Mut.", fill = "") +
  scale_x_discrete(labels = c("", "")) + guides(fill=FALSE) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20))

one_reldellethalsize <- ggplot(onestep_nonmelt, aes(x = pop, y = AvgDelLethalSize/BaseFitness, fill = pop)) + geom_boxplot(notch = T) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  labs(x = "", y = "Relative Fitness of Del+Lethal Mut.", fill = "") +
  scale_x_discrete(labels = c("", "")) + guides(fill=FALSE) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20))

one_alldel
one_reldelsize
one_reldellethalsize

```

Figure 4, showing the distribution of fitness effects from one to four step mutants.
```{r}

stepcoltypes <- cols(
  .default = col_double(),
  X1 = col_integer(),
  X11 = col_integer(),
  X12 = col_integer(),
  X15 = col_integer(),
  X21 = col_integer(),
  X22 = col_integer(),
  X23 = col_integer(),
  X24 = col_integer(),
  X25 = col_integer(),
  X26 = col_integer(),
  X27 = col_integer(),
  X28 = col_integer(),
  X29 = col_character(),
  X30 = col_character(),
  X31 = col_character(),
  X32 = col_character()
)

stepcolnames <- c(
  X1 = "Update",
  X2 = "Lethal",
  X3 = "Del", #Note the change here. 
  X4 = "Slt.Deleterious",
  X5 = "Deleterious", # "Any Deleterious" in other dataframes.
  X6 = "Neutral",
  X7 = "Beneficial",
  X8 = "AvgBenSize",
  X9 = "AvgDelSize",
  X10 = "AvgDelLethalSize",
  X11 = "TestedMutants",
  X12 = "Distance",
  X13 = "BaseFitness",
  X14 = "BaseMerit",
  X15 = "BaseGestation",
  X16 = "PeakFitness",
  X17 = "AvgFitness",
  X18 = "AvgSqFitness",
  X19 = "TotalS",
  X20 = "TotalComplex",
  X21 = "PLethalEpi",
  X22 = "PSynEpi",
  X23 = "PAntagEpi",
  X24 = "PNoEpi",
  X25 = "AvgSynEpiSize",
  X26 = "AvgAntagEpiSize",
  X27 = "AvgSizeNoEpi",
  X28 = "TotalEpiCount",
  X29 = "SuperRep",
  X30 = "StepNum",
  X31 = "Rep",
  X32 = "Duplicate"
)

frls_popA <- read_delim("./landscape/final_run_landscape_long_Fit.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)
frls_popB <- read_delim("./landscape/final_run_landscape_long_Flat.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)

frls_popA$pop <- "Fit"
frls_popB$pop <- "Flat"
frls_combo <- rbind(frls_popA, frls_popB)
frls_combo <- plyr::rename(frls_combo, stepcolnames)

#frls_melted <- melt(frls_combo[c(2,3,4,5,6,7,30,31,33)], id.vars = c("pop", "StepNum", "Rep")) Lethal, Del, SltDel, AnyDel, Neut, Ben.

frls_melted <- melt(frls_combo[c(2,5,6,7,30,31,33)], id.vars = c("pop", "StepNum", "Rep"))  #Lethal, AnyDel, Neut, Ben.

effect_bplots <- ggplot(frls_melted, aes(x = StepNum, y = value, fill = pop)) +
  geom_boxplot(notch = T, position = position_dodge(0.9)) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  labs(x = "", y = "Fraction of Mutations", title = "Summarized Distribution of Fitness Effects", fill = "") + 
  scale_x_discrete(labels=c("1", "2", "3", "4")) +
  xlab("Distance") +
  facet_grid(. ~ variable) +
  scale_y_log10() #actually makes Neut and Ben more readable without killing Lethal and Del too much. log10 makes lethal and del unreadable. None makes neut/ben difficult to read.

ggsave(effect_bplots, filename = "Fig4DFE.pdf", device = cairo_pdf, width = 8, height = 5)
effect_bplots
```

Alpha+Beta plots for each replicate.
```{r}
stepcoltypes <- cols(
  .default = col_double(),
  X1 = col_integer(),
  X11 = col_integer(),
  X12 = col_integer(),
  X15 = col_integer(),
  X21 = col_integer(),
  X22 = col_integer(),
  X23 = col_integer(),
  X24 = col_integer(),
  X25 = col_integer(),
  X26 = col_integer(),
  X27 = col_integer(),
  X28 = col_integer(),
  X29 = col_character(),
  X30 = col_character(),
  X31 = col_character(),
  X32 = col_character()
)

stepcolnames <- c(
  X1 = "Update",
  X2 = "Lethal",
  X3 = "Deleterious",
  X4 = "Slt.Deleterious",
  X5 = "AnyDel",
  X6 = "Neutral",
  X7 = "Beneficial",
  X8 = "AvgBenSize",
  X9 = "AvgDelSize",
  X10 = "AvgDelLethalSize",
  X11 = "TestedMutants",
  X12 = "Distance",
  X13 = "BaseFitness",
  X14 = "BaseMerit",
  X15 = "BaseGestation",
  X16 = "PeakFitness",
  X17 = "AvgFitness",
  X18 = "AvgSqFitness",
  X19 = "TotalS",
  X20 = "TotalComplex",
  X21 = "PLethalEpi",
  X22 = "PSynEpi",
  X23 = "PAntagEpi",
  X24 = "PNoEpi",
  X25 = "AvgSynEpiSize",
  X26 = "AvgAntagEpiSize",
  X27 = "AvgSizeNoEpi",
  X28 = "TotalEpiCount",
  X29 = "SuperRep",
  X30 = "StepNum",
  X31 = "Rep",
  X32 = "Duplicate"
)
frls_popA <- read_delim("./landscape/final_run_landscape_long_Fit.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)
frls_popB <- read_delim("./landscape/final_run_landscape_long_Flat.dat",  " ", escape_double = FALSE, col_names = FALSE, comment = "#", trim_ws = TRUE, skip = 1, col_types = stepcoltypes)

frls_popA$pop <- "Fit"
frls_popB$pop <- "Flat"
frls_combo <- rbind(frls_popA, frls_popB)
frls_combo <- plyr::rename(frls_combo, stepcolnames)

frls_combo$RunName <- paste(frls_combo$Rep, frls_combo$pop, sep ="_")

combo_relavgfit <- ggplot(data = frls_combo) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  geom_boxplot(aes(x = StepNum, y = frls_combo$AvgFitness / frls_combo$BaseFitness, fill = pop), notch = TRUE) + 
  labs(x = "Distance", y = "Avgerage Fitness / Base Fitness", fill = "") +
  scale_x_discrete(labels = c("1", "2", "3", "4"))

ggsave(combo_relavgfit, filename = "AvgRelFitDist.pdf", device = cairo_pdf, width = 9, height = 5)

combo_reldelsize <- ggplot(data = frls_combo) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  geom_boxplot(aes(x = StepNum, y = frls_combo$AvgDelSize / frls_combo$BaseFitness, fill = pop), notch = TRUE) + 
  labs(x = "Distance", y = "Deleterious Size / Base Fitness", fill = "") +
  scale_x_discrete(labels = c("1", "2", "3", "4"))

combo_reldellethalsize <- ggplot(data = frls_combo) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  geom_boxplot(aes(x = StepNum, y = frls_combo$AvgDelLethalSize / frls_combo$BaseFitness, fill = pop), notch = TRUE) + 
  labs(x = "Distance", y = "Del+Lethal Size / Base Fitness", fill = "") +
  scale_x_discrete(labels = c("1", "2", "3", "4"))

combo_reldelsize
combo_reldellethalsize
ggsave(filename = "RelDelSize.pdf", plot = combo_reldelsize, device = cairo_pdf, width = 10, height = 8)
ggsave(filename = "RelDelLethalSize.pdf", plot = combo_reldellethalsize, device = cairo_pdf, width = 10, height = 8)

```


Calculate all of the alphas and betas using the DFE data. Output plots. Make a new dataframe containing all of the alphas and betas.
```{r}
mut_fit_decay <- function(dist, Alpha, Beta) {
  -Alpha*dist - Beta * dist^2
}

setwd("./alpha_fits_dfe")

alpha_df <- tibble(RunName = character(), Alpha = double(), Beta = double(), pop = character())

for (repl in unique(frls_combo$Rep)) {
  fit_fit <-nls(formula = log(AvgFitness/BaseFitness) ~ -alpha*Distance-beta*Distance^2, data = filter(frls_combo, RunName == paste(repl, "_Fit", sep = "")), start = c(alpha = 1, beta = 0.01), control = nls.control(tol = 0.005, warnOnly = TRUE))
  fit_flat <-nls(formula = log(AvgFitness/BaseFitness) ~ -alpha*Distance-beta*Distance^2, data = filter(frls_combo, RunName == paste(repl, "_Flat", sep = "")), start = c(alpha = 1, beta = 0.01), control = nls.control(tol = 0.005, warnOnly = TRUE))
  
  alphaplt <- ggplot() + 
    geom_point(aes(x = Distance, y = log(AvgFitness/BaseFitness)), data = filter(frls_combo, RunName == paste(repl, "_Fit", sep = ""))) +
    geom_point(aes(x = Distance, y = log(AvgFitness/BaseFitness)), data = filter(frls_combo, RunName == paste(repl, "_Flat", sep = ""))) +
    stat_function(fun = mut_fit_decay, args = list(Alpha = coef(fit_fit)[1], Beta = coef(fit_fit)[2]), col = 'dodgerblue', data = filter(frls_combo, RunName == paste(repl, "_Fit", sep = ""))) +
    stat_function(fun = mut_fit_decay, args = list(Alpha = coef(fit_flat)[1], Beta = coef(fit_flat)[2]), col = 'firebrick1', data = filter(frls_combo, RunName == paste(repl, "_Flat", sep = ""))) +
    labs(title = repl, y = expression(log(W[avg]/W[base]))) +
    annotate(geom = "text", x = 2.0, y = mut_fit_decay(4, coef(fit_fit)[1], coef(fit_fit)[2])*0.9, label = paste("Fit alpha = ", round(coef(fit_fit)[1], 5), "\nFit beta = ", round(coef(fit_fit)[2], 5))) +
    annotate(geom = "text", x = 2.0, y = mut_fit_decay(4, coef(fit_fit)[1], coef(fit_fit)[2]), label = paste("Flat alpha = ", round(coef(fit_flat)[1], 5), "\nFlat beta = ", round(coef(fit_flat)[2], 5))) #+
    #ylim(0, 1)
  
  alpha_df <- add_row(alpha_df, RunName = repl, Alpha = coef(fit_fit)[1], Beta = coef(fit_fit)[2], pop = "Fit")
  alpha_df <- add_row(alpha_df, RunName = repl, Alpha = coef(fit_flat)[1], Beta = coef(fit_flat)[2], pop = "Flat")
  
  ggsave(plot = alphaplt, filename = paste(repl, ".png", sep = ""), device = 'png', width = 7, height = 7)
}

megaplot <- ggplot() + xlim(1, 4) + labs(x = "Distance", y = expression(W[avg]/W[base]))

for (repl in unique(alpha_df$RunName)) {
  dat_fit <- filter(alpha_df, RunName == repl, pop == "Fit")
  dat_flat <- filter(alpha_df, RunName == repl, pop == "Flat")
  megaplot <- megaplot + stat_function(fun = mut_fit_decay, col = 'dodgerblue', data = dat_fit, args = list(Alpha = dat_fit$Alpha, Beta = dat_fit$Beta), alpha = 0.9)
  megaplot <- megaplot + stat_function(fun = mut_fit_decay, col ="firebrick1", data = dat_flat, args = list(Alpha = dat_flat$Alpha, Beta = dat_flat$Beta), alpha = 0.9)
}

ggsave(plot = megaplot, filename = "CombinedAlphaBetaPlot.pdf", device = cairo_pdf)
```

Figure 5. Comparison of Alpha and Beta for each treatment.
```{r}

alpha_comp <- ggplot(data = alpha_df) +
  geom_boxplot(notch = TRUE, aes(x = pop, y = Alpha, fill = pop)) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  guides(fill = FALSE) +
  labs(x = "", y = expression(alpha)) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) 

beta_comp <- ggplot(data = alpha_df) +
  geom_boxplot(notch = TRUE, aes(x = pop, y = Beta, fill = pop)) +
  scale_fill_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) +
  geom_hline(yintercept = 0, linetype = 2) +
  guides(fill = FALSE) +
  labs(x = "", y = expression(beta)) +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) 

beta_corr_fit <- lm(Beta ~ Alpha, data = alpha_df) #nls(Beta ~ I((a*Alpha^2)+(b*Alpha)+c), data = alpha_df, start = list(a = 1, b = 1, c = 0)) insignificant "a"" term.

beta_fn <- function(alph) {
  p = coef(beta_corr_fit)
  return(p[2]*alph + p[1])
}

alpha_beta_corr <- ggplot(data = alpha_df) +
  geom_point(aes(x = Alpha, y = Beta, col = pop)) +
  scale_color_manual(values = c(Fit = "dodgerblue", Flat = "firebrick1")) + 
  stat_function(mapping = aes(x = Alpha, y = Beta), geom = "line", fun = beta_fn) +
  labs(x = expression(alpha), y = expression(beta), col = "") +
  theme(axis.text=element_text(size=18), legend.text=element_text(size=18), title=element_text(size=20), axis.title=element_text(size=20)) 

alpha_comp
beta_comp
alpha_beta_corr

alpha_sig <- wilcox.test(filter(alpha_df, pop == "Fit")$Alpha, filter(alpha_df, pop == "Flat")$Alpha)
beta_sig <- wilcox.test(filter(alpha_df, pop == "Fit")$Beta, filter(alpha_df, pop == "Flat")$Beta)
alpha_sig$p.value
beta_sig$p.value

combo_alphabeta <- ggdraw() + draw_plot(alpha_comp, 0, 0, 0.45, 1) + draw_plot(beta_comp, 0.45, 0, 0.5, 1) + draw_plot_label(label = c("a", "b"), c(0, 0.45), c(1, 1))

combo_alphabeta
ggsave(combo_alphabeta, filename = "Fig5AlphaBeta.pdf", device = cairo_pdf, width = 10, height = 5)
ggsave(alpha_beta_corr, filename = "AlphaBetaCorr.pdf", device = cairo_pdf, width = 10, height = 8)

```

Counting successful competitions. Successful competitions are ones in which the flat organism reached a frequency of 0.95 in three of five replicates for at least one mutation rate. Note that almost all flat organisms outperform the fit ones at high mutation rates, but to a lesser degree.
```{r}
comp_summary_names <- c(
  X1 = "Replicate",
  X2 = "Successful",
  X3 = "Mu"
)

comp_summary_types <- cols(
  Replicate = col_character(),
  Successful = col_character(),
  Mu = col_double()
)

sof_compeitions_bm0 <- read_csv("./competition/sof_compeitions_bm0.csv", col_names = comp_summary_names, col_types = comp_summary_types)

num_successful <- length(unique(filter(sof_compeitions_bm0, Successful == "True")$Replicate))
cat("Number of successful genotype pairs:", num_successful)

```
